\documentclass[11pt]{article}  

\usepackage{jwstproposaltemplate}
\usepackage{xcolor}
\usepackage[pdftex]{graphics,graphicx}
\usepackage{float} %enables forcing figures to sit where you want them with [H]
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{caption}
\captionsetup{belowskip=0pt}
\captionsetup{font=footnotesize,skip=0pt}

% bibliography-relevant packages
\usepackage[sort&compress,numbers]{natbib}
\usepackage{paralist}
\setlength{\bibsep}{0.0pt}

% commands to make all the short journal titles
% I'm sure there is a list somewhere, and/or a smarter way to do this
\newcommand\araa{Annu.~Rev.~Astron.~Astrophys.}%
\newcommand\arep{Annu.~Rev.~Earth~Planet.~Sci.}%
\newcommand\aj{Astron.~J.}%
\newcommand\apjl{Astrophys.~J.~Lett.}%
\newcommand\apj{Astrophys.~J.}%
\newcommand\aap{Astron.~Astrophys.}%
\newcommand\grl{Geophys.~Res.~Lett.}%
\newcommand\icarus{Icarus}%
\newcommand\jgr{J. Geophys.~Res.}%
\newcommand\mnras{Mon.~Not.~Roy.~Astron.~Soc.}%
\newcommand\nat{Nature}%
\newcommand\pasp{Pub.~Astron.~Soc.~Pac.}%
\newcommand\planss{Planet.~Space~Sci.}%
\newcommand\psj{Planet.~Sci.~J.}%
\newcommand\ptrsa{Philos.~Trans.~R.~Soc.~A}%
\newcommand\ssr{Space~Sci.~Rev.}%

\begin{document}

\begin{center}
	\textbf{Very Compressed Citations with xtrashort.bst}
\end{center}

\justification

Nobody knows why institutions still force you to compress references and make them smaller font in order to fit on a page. Some institutions have come around to excluding references in page limits, but for those that haven't, there is this bst file. That's a lot of citations in a small space!\citep{akins23, allison91, arras21, atreya20, aurnou07, beebe05, brogan18, lellouch07, sherjal95, teca}!

Hopefully the in-line comments are clear in both this file and in the .bst file, which I modified from apalike.bst. Big thanks to Yasmeen Asali for sharing that she had hacked .bst files for similar purposes before.

Not everything works perfectly yet; something should be done about e.g. conference proceedings like \citep{thatte15} but I didn't want to deal with it.

% modified apalike bst, with help from Yasmeen Asali at .Astronomy 12, Flatiron Institue, NYC
\bibliographystyle{apalike-xtrashort}

% condensed bibliography formatting via paralist enum environment
% see https://latex.org/forum/viewtopic.php?t=5953
\renewenvironment*{thebibliography}{
   \pointlessenum
   \begin{inparaenum}
   \renewcommand\makelabel[1]{  \textbf{[##1]}}
}{\end{inparaenum}}

% left align to remove weird spacing issues from forcing justified
% although some of the kerning could still use some work
\begin{flushleft}
% make reference fontsize smaller
\footnotesize{
\textit{References:}
\bibliography{sample}{} 
}
\end{flushleft}

\vspace{2cm}
\noindent\textit{
Author: Ned Molter, emolter@berkeley.edu, 6 October 2023
}

\end{document}

\endinput